Multilocus Genotype And Mycelial Compatability Group Assessment

### 2017-08-03 doc/RMD/mlg-mcg.Rmd
update visNetwork stuff

mcg_mlg_graph
if (!interactive()){
  ggsave(plot = mcg_mlg_graph, filename = file.path(PROJHOME, "results/figures/publication/FigureS2.pdf"), 
       width = 88*3, height = 88*3.5, units = "mm")
}

@@

make_rgb <- function(x, alpha = 1){
  out <- col2rgb(x, alpha = TRUE)
  out[4, ] <- floor(out[4, ]*alpha)
  out      <- apply(out, 2, paste, collapse = ", ")
  paste0("rgba(", out, ")")
}
vg <- g %>%
  set_vertex_attr("size", value = osize) %>%
  set_vertex_attr("value", value = osize) %>%
  set_vertex_attr("color", value = viridis(4)[as.integer(factor(the_communities$comm))]) %>%
  set_vertex_attr("shape", value = ifelse(V(.)$type == "Multilocus Genotype", "triangle", "circle")) %>%
  set_edge_attr("width", value = E(.)$weight) %>%
  toVisNetworkData()
vg$nodes <- vg$nodes %>% 
  group_by(id) %>%
  mutate(color = list(list(background = make_rgb(color, 0.8), 
                      border = make_rgb(rep("black", n()), 0.8),
                      highlight = list(background = make_rgb(color),
                                       border = make_rgb(rep("black", n()))
                                       )
                      )))
vgn <- visNetwork(nodes = vg$nodes, edges = vg$edges,# height = "500px", 
                  main = "Relation of Multilocus Genotypes and MCGs")
set.seed(2017-05-03)

vgn %>%
  visIgraphLayout("layout_nicely") %>%
  visOptions(highlightNearest = list(enabled = TRUE, hover = TRUE), 
             nodesIdSelection = TRUE)

>>>>

mcg_mlg_graph
if (!interactive()){
  ggsave(plot = mcg_mlg_graph, filename = file.path(PROJHOME, "results/figures/publication/FigureS2.pdf"), 
       width = 88*3, height = 88*3.5, units = "mm")
  tmp <- new.env()
  assign("mcg_mlg_igraph", g, envir = tmp)
  assign("mcg_mlg_gg", mcg_mlg_graph, envir = tmp)
  V(tmp$mcg_mlg_igraph)$size <- osize
  save(list = ls(envir = tmp), 
       envir = tmp, 
       file = file.path(PROJHOME, "data", "mcg-mlg-graph.rda"))
}

@@

make_rgb <- function(x, alpha = 1){
  out <- col2rgb(x, alpha = TRUE)
  out[4, ] <- floor(out[4, ]*alpha)
  out      <- apply(out, 2, paste, collapse = ", ")
  paste0("rgba(", out, ")")
}
community_colors <- viridis::viridis(4, direction = -1)[as.integer(factor(the_communities$comm))]
vg <- g %>%
  set_vertex_attr("size", value = osize * 10) %>%
  set_vertex_attr("value", value = osize) %>%
  set_vertex_attr("label", value = NULL) %>%
  set_vertex_attr("color", value = community_colors) %>%
  set_vertex_attr("shape", value = ifelse(V(.)$type == "Multilocus Genotype", "triangle", "dot")) %>%
  set_edge_attr("width", value = E(.)$weight) %>%
  toVisNetworkData()
vg$nodes <- vg$nodes %>% 
  dplyr::group_by(id) %>%
  dplyr::mutate(color = list(list(background = make_rgb(color, 0.8), 
                      border = make_rgb(rep("black", n()), 0.8),
                      highlight = list(background = make_rgb(color),
                                       border = make_rgb(rep("black", n()))
                                       )
                      ))) %>%
  dplyr::mutate(title = paste0("<p>",
                               "<i>", type, " ", gsub("MLG.", "", id), "</i><br>",
                               "<b>Community: ", community, "</b><br>",
                               "<b>N: ", size/10, "</b><br>",
                               "</p>")
                )
vg$edges <- vg$edges %>%
  dplyr::mutate(title = paste0("<p>",
                        "<b>Mycelial Compatibility Group: ", from, "</b><br>",
                        "<b>Multilocus Genotype: ", gsub("MLG.", "", to), "</b><br>",
                        "<b>N: ", weight, "</b>",
                        "</p>")
         )
vgn <- visNetwork(nodes = vg$nodes, edges = vg$edges,# height = "500px", 
                  main = "Relation of Multilocus Genotypes and MCGs")
set.seed(2017-05-03)

vgn %>%
  # visIgraphLayout("layout_nicely") %>% # activate this for a poseable network
  visNodes(label = NULL, shadow = TRUE) %>%
  visOptions(highlightNearest = list(enabled = TRUE, hover = TRUE), 
             nodesIdSelection = TRUE)
